Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-12 talk/dls2012/paper.tex
seems we don't use \url yet

Mike Pall pioneered a solution to address this problem in the context of a
dynamic language using a tracing JIT compiler. He published his algorithm and
its rationale in 2009~\cite{pall_luajit_2009} and implemented it in LuaJIT
2.0\footnote{\url{http://luajit.org/}}, an open source JIT compiler for the Lua
language. His approach allows to reuse all forward pass
optimizations to achieve loop invariant code motion and other loop-related
optimizations, which greatly simplifies the implementation. Using this scheme
one does not need to change the underlying optimization much to get these
advantages. We have implemented the same approach in PyPy's tracing JIT
compiler the results of which we present here.

>>>>

Mike Pall pioneered a solution to address this problem in the context of a
dynamic language using a tracing JIT compiler. He published his algorithm and
its rationale in 2009~\cite{pall_luajit_2009} and implemented it in LuaJIT
2.0\footnote{\texttt{http://luajit.org/}}, an open source JIT compiler for the Lua
language. His approach allows to reuse all forward pass
optimizations to achieve loop invariant code motion and other loop-related
optimizations, which greatly simplifies the implementation. Using this scheme
one does not need to change the underlying optimization much to get these
advantages. We have implemented the same approach in PyPy's tracing JIT
compiler the results of which we present here.
